TBD

### 2021-03-22 outputs/paper/paper.Rmd
Add Power analysis

@@

>>>>

# install.packages ("gmodels")
library (gmodels)

# install.packages("pwr")
library(pwr)

@@

## Power Analysis
```{r, echo = FALSE, message = FALSE}
dfPwr <-
  dfBehavModel %>%
  select('cond',
         'response') %>%
  filter(cond == 0 | cond == 1)

CrossTable(dfPwr$cond, dfPwr$response, chisq=TRUE, format=c("SPSS"))
```

```{r, echo = FALSE, message = FALSE}
freqByCond <-
  dfBehavModel %>%
  select('cond',
         'response') %>%
  filter(cond == 0 | cond == 1) %>%
  group_by(cond, response) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

propNoMoneyReturned <- freqByCond$freq[2]
proMoneyReturned <- freqByCond$freq[4]

# Reference Code: https://rdrr.io/cran/pwr/man/ES.h.html
effectSize <- 2 * asin(sqrt(propNoMoneyReturned)) - 2 * asin(sqrt(proMoneyReturned))

### Two-sample test for proportions (Unequal sample sizes)
# Reference Code:https://cran.r-project.org/web/packages/pwr/vignettes/pwr-vignette.html
# Reference: Conventional effect size from Cohen (1982)
pwr.2p.test(h = effectSize, sig.level = 0.05, power = 0.8)
```
